\input{title.tex}

### 2023-07-31 docs/papers/01_manuscript/04_discussion.tex
fix(project): :memo: change nameref into ref

Our results also corroborate some intuitive deductions of the hypothesis.
Firstly, we found significant correlations between current and changed water use after the 87-WAS, which suggests that the key stakeholders (such as Neimeng, Henan, and Shandong), were more likely to be affected by the institutional change.\
Secondly, a theoretical marginal benefit analysis (see \textit{\nameref{secS4}}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
Finally, since the YRCC could forcibly coordinate stakeholders by water quota licenses for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.

>>>>

Our results also corroborate some intuitive deductions of the hypothesis.
Firstly, we found significant correlations between current and changed water use after the 87-WAS, which suggests that the key stakeholders (such as Neimeng, Henan, and Shandong), were more likely to be affected by the institutional change.\
Secondly, a theoretical marginal benefit analysis (see \textit{\ref{secS4}}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
Finally, since the YRCC could forcibly coordinate stakeholders by water quota licenses for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.

### 2023-07-31 docs/papers/01_manuscript/06_methods.tex
fix(project): :memo: change nameref into ref

Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $D = 5$ principal components.
Previous study has proved that combining PCA and DSC can lead to a more robust causal inference~\cite{bayani2021}.
We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different. Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure\ref{fig:elbow}}).
Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.

>>>>

Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $D = 5$ principal components.
Previous study has proved that combining PCA and DSC can lead to a more robust causal inference~\cite{bayani2021}.
We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different. Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\ref{secS2}~Figure\ref{fig:elbow}}).
Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.

### 2023-07-31 docs/papers/01_manuscript/out/compiled_v-2.0.2.tex
fix(project): :memo: change nameref into ref

In methodology, we explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
Firstly, we used data on changes in official documents following two institutional shifts (the 87-WAS and the 98-UBR) to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008, by abstracting them into SES structures motifs (or building blocks, see \textit{\nameref{sec:structures}}).
We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\nameref{sec:DSC}} and \textit{\nameref{secS2}}).
This approach allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.
Finally, we further developed an approach for marginal benefits analysis, to interpret the underlying processes of the match and mismatched institutions based on SESs structures (\textit{\nameref{sec:model}}).

@@

\begin{figure*}[!t]
	\includegraphics[width=\linewidth]{diagrams/diagram.pdf}
	\caption{
		% 黄河流域的制度变迁与经济社会结构差异。
		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{\nameref{secS1}} Table~\ref{tab:quota}). The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
		\textbf{B.} Provincial administrative agencies are the major stakeholders. Since the 87-WAS, with surface water withdrawal from the Yellow River restricted by specific quotas, each stakeholder plan and use water resources for development. However, the natural hydrological processes are connected. Although the institutions focus mainly on surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur. and Gro.') through systematic socio-hydrological processes within the YRB. The YRCC only monitors water withdrawals at that time.
		\textbf{C.} Institutional shifts and following structures changes (details in \textit{\nameref{secS1}}). (1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of Yellow River, denoted by the blue circles). (2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota. (3) Since the 98-UBR, stakeholders have to apply for water use licenses from the YRCC (the connections between the red and yellow circles).
	}
	\label{fig:structure}
\end{figure*}

% 制度变动综述
The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{sec:yrb}} and \textit{\nameref{secS1}}).
Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
The YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
To shrink water deficits, in 87-WAS, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
Simultaneously, according to the extracted information from documents of the 87-WAS issued by national ministries, the YRCC started to report water use in each reach.
As it was the first time the responsibility of the YRCC involved water use, this introduced new links between the YRCC and the ecological nodes (Figure~\ref{fig:structure}~C).
However, the controversial 87-WAS did not resolve water depletion.
In 1998, another strategy (98-UBR) was developed to strengthen the responsibilities of the YRCC for integrated managing water use.
Information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license to YRCC instead of direct access to the Yellow River water.
Thus, the YRCC has been linked to the provinces since 1998 (Figure~\ref{fig:structure}~C).
% 因此，两次制度转换重塑了，形成了三个由社会行动者和生态节点连接而成的一般性结构
As result, the two institutional shifts reshaped SES structures, leading to three general structures linked by social actors and ecological nodes (Figure~\ref{fig:structure}~C).

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
	\caption{
		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
	\label{fig:model}
\end{figure}

For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water, leading to higher water use.
Furthermore, water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under a unified allocation.

@@

% \subsection{CAUSES OF INSTITUTIONAL IMPACTS}
% \subsection{}
\label{discussion-1}
% discussion-1:
% 用水量的上升、下降-结果解读
% 制度对社会生态系统的结果产生影响在世界范围内都很普遍，
The influences of institutions on the outcomes of social-ecological systems (SESs) were widely reported worldwide, but few attempts to quantify their net effects \cite{cumming2020a}.
Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it by $5.75\%$.
The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present \cite{abadie2015,hill2021}.
However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}}~Table~\ref{tab:variables}).
On the contrary, the 98-UBR reduced water competition, so many studies attributed the restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.

@@

Our approach has some inevitable limitations.
First, the contributions of economic growth and institutional shifts are difficult to distinguish because of intertwined causality (institutional changes can also influence the relative economic variables);
and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions \cite{bodin2017b, ostrom2009, reyers2018})
Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.
For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system.
From these perspectives, two scenarios based on the marginal benefit analysis (see \textit{\nameref{secS5}}) can inspire institutional design on how to reduce mismatches.
For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.
In addition, policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to a changing SES context \cite{reyers2018}.

The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}}) \cite{yu2019}.
Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019e}.
Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\nameref{secS1}}).
Our analysis suggests that these initiatives can benefit by actively incorporating social-ecological matched building blocks when developing new institutions \cite{bodin2017b}.
Moreover, our research provides a cautionary tale of how institutions can create perverse incentives \cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.

@@

\subsection{Portraying structures}\label{sec:structures}
% 制度结构关系抽象
We apply the network \cite{bodin2017b} approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures. The network-based approach is to abstract connections between entities into links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details).
Besides the ecologically connected river reaches, the agents (provinces and the YRCC) are abstracted as nodes, and their required interactions regarding water use are summarized as links.
The 1987-WAS requires the YRCC to monitor each river's reach, while the 1998-UBR requires direct interactions (through water use licenses) between the YRCC and the provinces.
Therefore, we linked the YRCC unit to each ecological unit after 87-WAS and each province unit after the 98-UBR.
We tested whether focusing on SES structures rather than institutional details could reasonably explain the differences caused by institutional shifts in the YRB.

@@

Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components \textit{Appendix~\nameref{secS2}}. Bayan had proved that combining PCA and DSC can raise the robustness of causal inference \cite{bayani2021}. We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different. Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure~\ref{fig:elbow}}). Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.

@@

Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

>>>>

In methodology, we explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
Firstly, we used data on changes in official documents following two institutional shifts (the 87-WAS and the 98-UBR) to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008, by abstracting them into SES structures motifs (or building blocks, see \textit{\nameref{sec:structures}}).
We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\nameref{sec:DSC}} and \textit{\ref{secS2}}).
This approach allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.
Finally, we further developed an approach for marginal benefits analysis, to interpret the underlying processes of the match and mismatched institutions based on SESs structures (\textit{\nameref{sec:model}}).

@@

\begin{figure*}[!t]
	\includegraphics[width=\linewidth]{diagrams/diagram.pdf}
	\caption{
		% 黄河流域的制度变迁与经济社会结构差异。
		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{\ref{secS1}} Table~\ref{tab:quota}). The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
		\textbf{B.} Provincial administrative agencies are the major stakeholders. Since the 87-WAS, with surface water withdrawal from the Yellow River restricted by specific quotas, each stakeholder plan and use water resources for development. However, the natural hydrological processes are connected. Although the institutions focus mainly on surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur. and Gro.') through systematic socio-hydrological processes within the YRB. The YRCC only monitors water withdrawals at that time.
		\textbf{C.} Institutional shifts and following structures changes (details in \textit{\ref{secS1}}). (1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of Yellow River, denoted by the blue circles). (2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota. (3) Since the 98-UBR, stakeholders have to apply for water use licenses from the YRCC (the connections between the red and yellow circles).
	}
	\label{fig:structure}
\end{figure*}

% 制度变动综述
The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{sec:yrb}} and \textit{\ref{secS1}}).
Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
The YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
To shrink water deficits, in 87-WAS, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
Simultaneously, according to the extracted information from documents of the 87-WAS issued by national ministries, the YRCC started to report water use in each reach.
As it was the first time the responsibility of the YRCC involved water use, this introduced new links between the YRCC and the ecological nodes (Figure~\ref{fig:structure}~C).
However, the controversial 87-WAS did not resolve water depletion.
In 1998, another strategy (98-UBR) was developed to strengthen the responsibilities of the YRCC for integrated managing water use.
Information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license to YRCC instead of direct access to the Yellow River water.
Thus, the YRCC has been linked to the provinces since 1998 (Figure~\ref{fig:structure}~C).
% 因此，两次制度转换重塑了，形成了三个由社会行动者和生态节点连接而成的一般性结构
As result, the two institutional shifts reshaped SES structures, leading to three general structures linked by social actors and ecological nodes (Figure~\ref{fig:structure}~C).

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
	\caption{
		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\ref{secS4}}).}
	\label{fig:model}
\end{figure}

For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\ref{secS4}}).
Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water, leading to higher water use.
Furthermore, water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under a unified allocation.

@@

% \subsection{CAUSES OF INSTITUTIONAL IMPACTS}
% \subsection{}
\label{discussion-1}
% discussion-1:
% 用水量的上升、下降-结果解读
% 制度对社会生态系统的结果产生影响在世界范围内都很普遍，
The influences of institutions on the outcomes of social-ecological systems (SESs) were widely reported worldwide, but few attempts to quantify their net effects \cite{cumming2020a}.
Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it by $5.75\%$.
The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present \cite{abadie2015,hill2021}.
However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\ref{secS2}}~Table~\ref{tab:variables}).
On the contrary, the 98-UBR reduced water competition, so many studies attributed the restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.

@@

Our approach has some inevitable limitations.
First, the contributions of economic growth and institutional shifts are difficult to distinguish because of intertwined causality (institutional changes can also influence the relative economic variables);
and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions \cite{bodin2017b, ostrom2009, reyers2018})
Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.
For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system.
From these perspectives, two scenarios based on the marginal benefit analysis (see \textit{\ref{secS5}}) can inspire institutional design on how to reduce mismatches.
For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.
In addition, policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to a changing SES context \cite{reyers2018}.

The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\ref{secS1}}) \cite{yu2019}.
Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019e}.
Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\ref{secS1}}).
Our analysis suggests that these initiatives can benefit by actively incorporating social-ecological matched building blocks when developing new institutions \cite{bodin2017b}.
Moreover, our research provides a cautionary tale of how institutions can create perverse incentives \cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.

@@

\subsection{Portraying structures}\label{sec:structures}
% 制度结构关系抽象
We apply the network \cite{bodin2017b} approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures. The network-based approach is to abstract connections between entities into links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \ref{secS1}} for details).
Besides the ecologically connected river reaches, the agents (provinces and the YRCC) are abstracted as nodes, and their required interactions regarding water use are summarized as links.
The 1987-WAS requires the YRCC to monitor each river's reach, while the 1998-UBR requires direct interactions (through water use licenses) between the YRCC and the provinces.
Therefore, we linked the YRCC unit to each ecological unit after 87-WAS and each province unit after the 98-UBR.
We tested whether focusing on SES structures rather than institutional details could reasonably explain the differences caused by institutional shifts in the YRB.

@@

Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components \textit{Appendix~\ref{secS2}}. Bayan had proved that combining PCA and DSC can raise the robustness of causal inference \cite{bayani2021}. We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different. Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\ref{secS2}~Figure~\ref{fig:elbow}}). Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.

@@

Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\ref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\ref{secS5}}.

### 2023-07-31 docs/papers/04_response_letter/source/reviewer_2.tex
fix(project): :memo: change nameref into ref

\AR{} We appreciate your thoughtful suggestion about additional robustness checks for our Differenced Synthetic Control (DSC) method. However, we have chosen not to include further robustness checks in our revised manuscript for several reasons:

@@

\AR{} Thank you for your positive feedback on the comprehensiveness of the results, discussion, and comparisons in our paper. We're delighted to hear that you found this section satisfactory. Your kind words are greatly encouraging and motivate us to continue to improve our work. We hope that the revisions we have made in response to your helpful suggestions have improved the manuscript.

>>>>

\AR{} We appreciate your thoughtful suggestion about additional checks for our Differenced Synthetic Control (DSC) method. We now revised the term from ``robustness'' to ``efficiency'' based on the comments from the reviewer \#1, so we basically kept the tests section without additional approach for the following reasons:

@@

\AR{} Thank you for your positive feedback on the comprehensiveness of the results, discussion, and comparisons in our paper. We're delighted to hear that you found this section satisfactory. Your kind words are greatly encouraging and motivate us to continue to improve our work. We've still improved the discussion section, and we hope you'll find this even better.
